\pkg{hesim}: Health Economic Simulation Modeling and Decision Analysis

### 2021-07-12 manuscript.Rnw
Remove explicit print statements

<<tmat>>=
tmat <- rbind(
  c(NA, 1, 2),
  c(NA, NA, 3),
  c(NA, NA, NA)
)
colnames(tmat) <- rownames(tmat) <- c("Stable", "Progression", "Dead")
print(tmat)
@

@@

hesim_dat <- hesim_data(
  strategies = strategies,
  patients = patients,
  states = states
)
print(hesim_dat)
@

@@

<<labels_indiv>>=
labs_indiv <- get_labels(hesim_dat)
print(labs_indiv)
@

@@

<<ictstm_utility>>=
utility_tbl <- stateval_tbl(
  data.table(state_id = states$state_id,
             mean = c(.8, .6),
             se = c(0.02, .05)
  ),
  dist = "beta")
print(utility_tbl)
@

@@

<<ictstm_medcosts>>=
medcost_tbl <- stateval_tbl(
  data.table(state_id = states$state_id,
             mean = c(2000, 9500),
             se = c(2000, 9500)
  ),
  dist = "gamma")
print(medcost_tbl)
@

@@

<<ictstm_drugcost>>=
drugcost_tbl <- stateval_tbl(
  drugcost_dt,
  dist = "fixed")
print(drugcost_tbl)
@

@@

<<psm_drugcost>>=
drugcost_tbl <- stateval_tbl(
  drugcost_dt[time_start ==  0][, time_start := NULL],
  dist = "fixed")
print(drugcost_tbl)
@

>>>>

<<tmat>>=
tmat <- rbind(
  c(NA, 1, 2),
  c(NA, NA, 3),
  c(NA, NA, NA)
)
colnames(tmat) <- rownames(tmat) <- c("Stable", "Progression", "Dead")
tmat
@

@@

hesim_dat <- hesim_data(
  strategies = strategies,
  patients = patients,
  states = states
)
hesim_dat
@

@@

<<labels_indiv>>=
labs_indiv <- get_labels(hesim_dat)
labs_indiv
@

@@

<<ictstm_utility>>=
utility_tbl <- stateval_tbl(
  data.table(state_id = states$state_id,
             mean = c(.8, .6),
             se = c(0.02, .05)
  ),
  dist = "beta")
utility_tbl
@

@@

<<ictstm_medcosts>>=
medcost_tbl <- stateval_tbl(
  data.table(state_id = states$state_id,
             mean = c(2000, 9500),
             se = c(2000, 9500)
  ),
  dist = "gamma")
medcost_tbl
@

@@

<<ictstm_drugcost>>=
drugcost_tbl <- stateval_tbl(
  drugcost_dt,
  dist = "fixed")
drugcost_tbl
@

@@

<<psm_drugcost>>=
drugcost_tbl <- stateval_tbl(
  drugcost_dt[time_start ==  0][, time_start := NULL],
  dist = "fixed")
drugcost_tbl
@

### 2021-07-12 manuscript.tex
Remove explicit print statements

%% -- Illustrative example -----------------------------------------------------
\section{Illustrative example} \label{sec:illustrative-example}
We consider a three-state model commonly used in oncology. As shown in Figure~\ref{fig:three-state-model}, the three health states are stable disease (i.e., not progressed), progression, and death. Patients can transition to a more severe health state (stable $\rightarrow$ progression, stable $\rightarrow$ death, and progression $\rightarrow$ death) but cannot recover to a less severe health state. We assume that patients remain on first line (1L) treatment until progression, at which time they switch to a second line (2L) treatment.

@@

\begin{Schunk}
\begin{Sinput}
R> tmat <- rbind(
+    c(NA, 1, 2),
+    c(NA, NA, 3),
+    c(NA, NA, NA)
+  )
R> colnames(tmat) <- rownames(tmat) <- c("Stable", "Progression", "Dead")
R> print(tmat)
\end{Sinput}
\begin{Soutput}
            Stable Progression Dead
Stable          NA           1    2
Progression     NA          NA    3
Dead            NA          NA   NA
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> library("hesim")
R> library("data.table")
R> n_patients <- 1000
R> patients <- data.table(
+    patient_id = 1:n_patients,
+    age = rnorm(n_patients, mean = 45, sd = 7),
+    female = rbinom(n_patients, size = 1, prob = .51)
+  )
R> 
R> states <- data.table(
+    state_id = c(1, 2),
+    state_name = c("Stable", "Progression") 
+  )
R> 
R> strategies <- data.table(
+    strategy_id = 1:3,
+    strategy_name = c("SOC", "New 1", "New 2"),
+    soc = c(1, 0, 0),
+    new1 = c(0, 1, 0),
+    new2 = c(0, 0, 1)
+  )
R> 
R> hesim_dat <- hesim_data(
+    strategies = strategies,
+    patients = patients,
+    states = states
+  )
R> print(hesim_dat)
\end{Sinput}
\begin{Soutput}
$strategies
   strategy_id strategy_name soc new1 new2
1:           1           SOC   1    0    0
2:           2         New 1   0    1    0
3:           3         New 2   0    0    1

@@

\begin{Schunk}
\begin{Sinput}
R> labs_indiv <- get_labels(hesim_dat)
R> print(labs_indiv)
\end{Sinput}
\begin{Soutput}
$strategy_id
  SOC New 1 New 2 
    1     2     3

@@

\begin{Schunk}
\begin{Sinput}
R> utility_tbl <- stateval_tbl(
+    data.table(state_id = states$state_id,
+               mean = c(.8, .6),
+               se = c(0.02, .05)
+    ),
+    dist = "beta")
R> print(utility_tbl)
\end{Sinput}
\begin{Soutput}
   state_id mean   se
1:        1  0.8 0.02
2:        2  0.6 0.05
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> medcost_tbl <- stateval_tbl(
+    data.table(state_id = states$state_id,
+               mean = c(2000, 9500),
+               se = c(2000, 9500)
+    ),
+    dist = "gamma")
R> print(medcost_tbl)
\end{Sinput}
\begin{Soutput}
   state_id mean   se
1:        1 2000 2000
2:        2 9500 9500
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> drugcost_tbl <- stateval_tbl(
+    drugcost_dt,
+    dist = "fixed")
R> print(drugcost_tbl)
\end{Sinput}
\begin{Soutput}
    strategy_id state_id time_id time_start time_stop   est
 1:           1        1       1       0.00      0.25  2000
 2:           1        1       2       0.25       Inf  2000
 3:           1        2       1       0.00      0.25  1500
 4:           1        2       2       0.25       Inf  1200
 5:           2        1       1       0.00      0.25 12000
 6:           2        1       2       0.25       Inf 12000
 7:           2        2       1       0.00      0.25  1500
 8:           2        2       2       0.25       Inf  1200
 9:           3        1       1       0.00      0.25 15000
10:           3        1       2       0.25       Inf 15000
11:           3        2       1       0.00      0.25  1500
12:           3        2       2       0.25       Inf  1200
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> drugcost_tbl <- stateval_tbl(
+    drugcost_dt[time_start ==  0][, time_start := NULL],
+    dist = "fixed")
R> print(drugcost_tbl)
\end{Sinput}
\begin{Soutput}
   strategy_id state_id   est
1:           1        1  2000
2:           1        2  1500
3:           2        1 12000
4:           2        2  1500
5:           3        1 15000
6:           3        2  1500
\end{Soutput}
\end{Schunk}

>>>>

%% -- Illustrative example -----------------------------------------------------
\section{Simulation of model outcomes} \label{sec:model-simulation}
To demonstrate how \pkg{hesim} can be used to simulate outcomes from an economic model, we consider a three state model commonly used in oncology. As shown in Figure~\ref{fig:three-state-model}, the three health states are stable disease (i.e., not progressed), progression, and death. Patients can transition to a more severe health state (stable $\rightarrow$ progression, stable $\rightarrow$ death, and progression $\rightarrow$ death) but cannot recover to a less severe health state. We assume that patients remain on first line (1L) treatment until progression, at which time they switch to a second line (2L) treatment.

@@

\begin{Schunk}
\begin{Sinput}
> tmat <- rbind(
+   c(NA, 1, 2),
+   c(NA, NA, 3),
+   c(NA, NA, NA)
+ )
> colnames(tmat) <- rownames(tmat) <- c("Stable", "Progression", "Dead")
> tmat
\end{Sinput}
\begin{Soutput}
            Stable Progression Dead
Stable          NA           1    2
Progression     NA          NA    3
Dead            NA          NA   NA
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> library("hesim")
> library("data.table")
> n_patients <- 1000
> patients <- data.table(
+   patient_id = 1:n_patients,
+   age = rnorm(n_patients, mean = 45, sd = 7),
+   female = rbinom(n_patients, size = 1, prob = .51)
+ )
> 
> states <- data.table(
+   state_id = c(1, 2),
+   state_name = c("Stable", "Progression") 
+ )
> 
> strategies <- data.table(
+   strategy_id = 1:3,
+   strategy_name = c("SOC", "New 1", "New 2"),
+   soc = c(1, 0, 0),
+   new1 = c(0, 1, 0),
+   new2 = c(0, 0, 1)
+ )
> 
> hesim_dat <- hesim_data(
+   strategies = strategies,
+   patients = patients,
+   states = states
+ )
> hesim_dat
\end{Sinput}
\begin{Soutput}
$strategies
   strategy_id strategy_name soc new1 new2
1:           1           SOC   1    0    0
2:           2         New 1   0    1    0
3:           3         New 2   0    0    1

@@

\begin{Schunk}
\begin{Sinput}
> labs_indiv <- get_labels(hesim_dat)
> labs_indiv
\end{Sinput}
\begin{Soutput}
$strategy_id
  SOC New 1 New 2 
    1     2     3

@@

\begin{Schunk}
\begin{Sinput}
> utility_tbl <- stateval_tbl(
+   data.table(state_id = states$state_id,
+              mean = c(.8, .6),
+              se = c(0.02, .05)
+   ),
+   dist = "beta")
> utility_tbl
\end{Sinput}
\begin{Soutput}
   state_id mean   se
1:        1  0.8 0.02
2:        2  0.6 0.05
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> medcost_tbl <- stateval_tbl(
+   data.table(state_id = states$state_id,
+              mean = c(2000, 9500),
+              se = c(2000, 9500)
+   ),
+   dist = "gamma")
> medcost_tbl
\end{Sinput}
\begin{Soutput}
   state_id mean   se
1:        1 2000 2000
2:        2 9500 9500
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> drugcost_tbl <- stateval_tbl(
+   drugcost_dt,
+   dist = "fixed")
> drugcost_tbl
\end{Sinput}
\begin{Soutput}
    strategy_id state_id time_id time_start time_stop   est
 1:           1        1       1       0.00      0.25  2000
 2:           1        1       2       0.25       Inf  2000
 3:           1        2       1       0.00      0.25  1500
 4:           1        2       2       0.25       Inf  1200
 5:           2        1       1       0.00      0.25 12000
 6:           2        1       2       0.25       Inf 12000
 7:           2        2       1       0.00      0.25  1500
 8:           2        2       2       0.25       Inf  1200
 9:           3        1       1       0.00      0.25 15000
10:           3        1       2       0.25       Inf 15000
11:           3        2       1       0.00      0.25  1500
12:           3        2       2       0.25       Inf  1200
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> drugcost_tbl <- stateval_tbl(
+   drugcost_dt[time_start ==  0][, time_start := NULL],
+   dist = "fixed")
> drugcost_tbl
\end{Sinput}
\begin{Soutput}
   strategy_id state_id   est
1:           1        1  2000
2:           1        2  1500
3:           2        1 12000
4:           2        2  1500
5:           3        1 15000
6:           3        2  1500
\end{Soutput}
\end{Schunk}
